---
title: "Removing Character from Date - RStudio"
author: "stang3g"
date: "2022-11-24"
output: html_document
---

**The below steps will show you how to remove a character from a 'character variable' and then transform into a date variable.** 


**Loading libraries that will be used**  
```{r}
library(tidyverse)  

library(lubridate) # used to make variables into date 

```

**For this demo, Covid-19 data set from Johns Hopkins University will be used.**  
data source URF :<https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/> 

**Pulling in data urls and putting then in a vector**  
```{r}
url_in <- ("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/")  

file_names <- c("time_series_covid19_confirmed_US.csv",
                "time_series_covid19_confirmed_global.csv",
                "time_series_covid19_deaths_US.csv",
                "time_series_covid19_deaths_global.csv",
                "time_series_covid19_recovered_global.csv")  
library(stringr) 
urls <- str_c(url_in,file_names) 


```

**importing data from urls**    
```{r import_data, message=FALSE}
Us_cases <- read.csv(urls[1])
global_cases <- read.csv(urls[2])

```

**cleaning up global_cases table and create a new global table**  
pivot columns and changing variable names then creating a new table.
  
```{r}
global_cases2 <- global_cases %>%
  pivot_longer(cols = -c('Province.State',
                         'Country.Region', Lat, Long),
              names_to = "date",
              values_to = "cases") %>%
  select(-c(Lat,Long))
  

```

**Cleaning data by removing the x in the date variable from the data set**  
```{r}
global_cases2$date <-gsub("X","", as.character(global_cases2$date))
```

**first replace "." with "_" for the date variable so that you can convert to date value **  
```{r}
global_cases2$date <-gsub("[.]","-", (global_cases2$date))

```
**changing Char date to date variable**  
```{r}
library(lubridate)
global_cases2$date <- mdy(global_cases2$date)
```
